\documentclass[10pt]{article}
\input{../common/style.tex}

\begin{document}
\begin{paracol}{2}

% ===================== SIDEBAR =====================
\small
\resumename{Herberth Diego Ruas Caldeira}{Full Stack Developer}

\cvsection{Contact}
Montes Claros -- MG, Brazil\\
31 years old\\
+55 38 99127-6803\\
herberthcaldeira@gmail.com

\cvsection{Links}
LinkedIn:\\
\href{https://www.linkedin.com/in/herberth-caldeira-1a82791ba}{linkedin.com/in/herberth-caldeira}\\[4pt]
GitHub:\\
\href{https://github.com/HerberthCaldeira}{github.com/HerberthCaldeira}

\cvsection{Skills}
PostgreSQL, MySQL, SQLite, SQL, AWS, CI/CD, Docker, Linux, HTML, CSS, RESTful APIs, PHP, Laravel Framework, TDD (PHPUnit and Pest), Livewire, AlpineJs, React.js, Bootstrap, TailwindCSS, Node.js, TypeScript, JavaScript, Ansible, Design Patterns, MVC, Clean Code and Clean Architecture.

\cvsection{Education}
\textbf{Unimontes}\\
B.Sc. in Information Systems\\
\textit{01/2021 -- 06/2025}

\cvsection{Languages}
Portuguese (native)\\
English (intermediate)

\cvsection{Certifications}
OOPMentor --- Object-Oriented Software Design And Quality

\switchcolumn

% ===================== MAIN COLUMN =====================
\small
\cvsection{Summary}
Full Stack Developer with 6+ years of experience in web development, specialized in PHP/Laravel and the JavaScript/TypeScript ecosystem (React.js, Node.js). Experience building SaaS products, scalable RESTful APIs, and deployment automation with Docker, Ansible, and CI/CD.

\cvsection{Experience}

\jobentry{Full Stack Developer}{SoteroTech}{01/2023 -- 02/2025}
{\footnotesize\color{textgray}PostgreSQL, MySQL, Laravel Framework, Livewire, React.js, TDD (PHPUnit and Pest), Node.js, TypeScript, JavaScript, HTML, CSS, Docker and Ansible.\par\vspace{2pt}}
\begin{itemize}
  \item Developed a ticketing/service management system using Laravel Framework and Livewire.
  \item Built a SaaS product for a company in the education sector using Laravel Framework, React.js and TypeScript.
  \item Built a SaaS product for a company in the healthcare sector using Node.js and TypeScript.
  \item Integrated third-party services and libraries such as PagSeguro, Agora.io and Jitsi.
  \item Developed efficient and scalable RESTful APIs.
  \item Built Single-Page Applications (SPA) with React.js/TypeScript.
  \item Implemented real-time communication via WebSocket.
  \item Automated deployment and continuous integration to streamline the development workflow using Shell script, Ansible and GitHub Actions.
\end{itemize}

\jobentry{Full Stack Developer}{Talkee Digital}{06/2021 -- 06/2022}
{\footnotesize\color{textgray}Docker, PostgreSQL, HTML, CSS, Laravel Framework, JavaScript, TypeScript, React.js and InertiaJs.\par\vspace{2pt}}
\begin{itemize}
  \item Developed and optimized a CRM system.
  \item Built RESTful APIs with Laravel.
  \item Implemented Single-Page Applications (SPA) with React.js and TypeScript.
  \item Integrated with WhatsApp.
  \item Implemented real-time communication via WebSocket.
  \item Automated deployment with Shell Script and Ansible.
\end{itemize}

\jobentry{Full Stack Developer}{MedPlim Solutions em Tecnologia LTDA}{10/2017 -- 09/2020}
{\footnotesize\color{textgray}MySQL, HTML, CSS, PHP, JavaScript, jQuery, Laravel and CodeIgniter.\par\vspace{2pt}}
\begin{itemize}
  \item Developed a management system for medical clinics.
  \item Applied the MVC (Model-View-Controller) pattern to organize the codebase.
  \item Implemented dynamic interfaces with JavaScript, jQuery and AJAX.
  \item Implemented features to optimize appointment scheduling, patient service and the financial workflow of medical clinics.
\end{itemize}

\end{paracol}
\end{document}
